---
title: "Reproducible Pitch"
author: "Qiaohong"
date: "11/17/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Summary

* This deck introduces you to the shiny app I made that shows US election results per state.
* Red state - there are more votes to republicans than to democrats.
* Blue state - there are more votes to democrates than to republicans.
* White state - the votes are almost the same to both party candidates.
* The darker the blue/ red color is, the bigger the differences are in votes.

## Plot example
* Results for 2016 (Clinton v.s. Trump). In the shiny app you can see results from 2012 as well for comparison
* The app is [here](https://ciao.shinyapps.io/coursera_assignment/)
```{r}
library(ggplot2)
source("helper.R")
data <- readRDS("data/data_for_map.rds")
make_plot(data, "c_t")
```

## Tech details
* Plot was made with ggplot
* Data was pre-processed and uploaded.
* The function making plot is in helper.R to make the code neat.

## Reference links
* Election data was sourced from github [Emil Kierkegaard](https://github.com/Deleetdk/USA.county.data)
* The architect of the app was inspired by the [R Shiny tutorial](http://shiny.rstudio.com/tutorial/lesson5/)
* The ggplot code got some help from [here] (https://www.r-bloggers.com/us-state-maps-using-map_data/)
